Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-11 paper/paper.tex
edits fuzzers discussion
Made a pass on 7.1 Finding bugs in Hermes

\hermes is a JavaScript engine introduced by Facebook in 2019. According to its website, \hermes ``is a JavaScript engine optimized for fast start-up of React Native apps on Android''~\cite{hermes2020repo}.
Before testing \hermes with our both test transplantation and differential testing, we ran the Test262 conformance suite on the most recent version of \hermes, 0.5.0. We observed that only 26\% of the Test262 tests were passing at the \hermes project. When taking a closer look, we noticed that this high percentage of failing test was due to the a also high number of features not yet suported by \hermes. For instance, in its most recent release, \hermes still do not offer support for features such as Proxy, Promisse, and Async. For this reason (the low coverage of Test262 tests), we also opted not to include \hermes along with the other JavaScript engines. Since we only fuzz test files that pass in all engines, this would require us to significantly reduce the numbers of test used in the experiments.

We then ran both test transplantation and differential testing on \hermes. To do this work, we follow the same methodology described for the others JavaScript engines. When experimenting with test transplantation, we noted many errors when replaying the \smonkey testing stuite on \hermes. This happened because \smonkey has its own assertion framework, but \hermes did not interpret these assertions, resulting in failures in all test executions from this engine. These failures did not happen when the \smonkey tests were transplanted to the other engines, though. Overall, we found and repoted three bugs on \hermes using the test transplantation technique. One of them was confirmed by the \hermes maintainers. For one of the other bugs reported, the maintainer mentioned that the bug in question was regarding a feature not yet supported (a \texttt{return} statement outside the block scope). For the third one, the maintainers diverged regarding the proper implementation of one particular item of the specification (i.e., whether a numeric escape (non-octal-eight, \texttt{\textbackslash{8}}) should be allowed or not in strict mode. The issue was closed, but the maintainers opened a new one to discuss this matter. Among the discussions, it was interesting to observe that maintainers are aware that this feature is implemented by other engines such as \veight, \chakra, and \smonkey (yet they were unsure how they should treat it at \hermes).  As for the differential testing, we found and reported one bug on \hermes using \radamsa. As of this writing, this particular bug report was not yet addressed by any \hermes maintainer.

Overall, we noted that the use of test transplantation and differential testing could be effective techniques in discovering bugs in non-trivial JavaScript software systems, regardless of their maintenance scenario (that is, we found bugs in both extremely roubust and largely adopted engines and also on a recently introduced, with many non-supported official features, engine).

>>>>

\hermes is a JavaScript engine introduced by Facebook in 2019. According to its website, \hermes is ``a JavaScript engine optimized for fast start-up of React Native apps on Android''~\cite{hermes2020repo}.
Before applying \entente on \hermes for performing test transplantation and differential testing, we ran the Test262 conformance suite on the most recent version of \hermes, 0.5.0. We observed that only 26\% of the Test262 tests were passing at the \hermes project. When taking a closer look, we noticed that this high percentage of failing tests was due to the high number of features not yet suported by \hermes. For instance, in its most recent release, \hermes still does not offer support for features such as Proxy, Promisse, and Async. For this reason (the low coverage of Test262 tests), we opted not to include \hermes along with the other JavaScript engines. Since we only fuzz test files that pass in all engines, this would require us to significantly reduce the number of tests used in the experiments.

We then ran both test transplantation and differential testing on \hermes. To do this work, we follow the same methodology described for the others JavaScript engines. When experimenting with test transplantation, we noted many errors when replaying the \smonkey testing stuite on \hermes. This happened because \smonkey has its own assertion framework, but \hermes did not interpret these assertions, resulting in failures in all test executions from this engine. These failures did not happen when the \smonkey tests were transplanted to the other engines, though. Overall, we found and repoted three bugs on \hermes using the test transplantation technique. One of them was already confirmed by the \hermes maintainers. For one of the other bugs reported, the maintainer mentioned that the bug in question is related to a feature not yet supported (a \texttt{return} statement outside the block scope). For the third one, the maintainers diverged regarding the proper implementation of one particular item of the specification (i.e., whether a numeric escape (non-octal-eight, \texttt{\textbackslash{8}}) should be allowed or not in strict mode. The issue was closed, but the maintainers opened a new one to discuss this matter. By following the discussion, it was interesting to observe that maintainers are aware that this feature is implemented by other engines such as \veight, \chakra, and \smonkey (yet they were unsure how they should treat it at \hermes).  As for the differential testing, we found and reported one bug on \hermes using \radamsa. As of this writing, this particular bug report was not yet addressed by any \hermes maintainer.

Overall, we noted that the use of test transplantation and differential testing could be effective techniques in discovering bugs in non-trivial JavaScript software systems, regardless of their maintenance scenario (that is, we found bugs in both extremely roubust and largely adopted engines and also on a recently introduced one with many non-supported official features).
